
\begin{thebibliography}{99}



\bibitem{AW92} Aeyels, D. and J.L. Willems, Pole assignment for linear
time-invariant systems by periodic memoryless output feedback, {\em
Automatica}, Vol. 28, pp. 1159-1168, 1992.


\bibitem{AD} Anantharam, V. and C.A. Desoer, (1984), On the  stabilization
 of  Nonlinear systems, {\em IEEE Trans. on Automatic Control,} Vol. AC-29, pp. 
569-572.

\bibitem{AM}
Anderson, B.D.O. and J.B. Moore, (1981), Time-varying feedback laws for
decentralized control, {\em IEEE Trans. on Automatic Control,} Vol.
AC-26, pp. 1133-1138.

\bibitem{BP} Bamieh, B. and J.B. Pearson, A general framework for linear
periodic systems with applications to $H^\infty$ sampled data control, {\em
IEEE Trans. on Automatic Control,} Vol. AC-37, No. 4, pp. 418-435, 1992.

\bibitem{BP2} Bamieh, B. and J.B. Pearson, The $H_2$ problem  for  sampled data
systems, {\em System  and  Control Letters,} Vol. 19, (1992) pp. 1-12.


\bibitem{Ba}
Bartle, R.,  {\em The Elements of  Integration}, John Wiley and Sons, 1966.


%\bibitem{B} Brockett, R.W., Asymptotic Stability and feedback stabilization,
%in {\em Differential Geometric Control Theory} (R.W. Brockett, R.S. Millman
%and H.J. Sussmann Eds.) Birkhauser, Basel-Boston, 1983.


\bibitem{CD2}
Callier, F.M.  and C.A. Desoer,  {\em Linear System Theory}, Springer  Verlag, 1991.

\bibitem{CD}
Chapellat, H. and M. Dahleh, Analysis of time-varying control
strategies for optimal disturbance rejection and robustness,  {\em IEEE
Trans. on Automatic Control,} Vol. AC-37, (1992) pp. 1734-1745.


\bibitem{CF} Chen, T. and B. Francis, Input-Output  Stability of  Sampled-data
Systems,  {\em IEEE Trans. on Automatic Control,} Vol. AC-36, pp. 50-58, 1991.

\bibitem{CF2} Chen, T. and B. Francis, Linear time varying  $H_2$-optimal control
of sampled data systems,  {\em Automatica,} 27 (1991) pp. 963-974.


\bibitem{CFr} Chen, T. and Francis, {\em Optimal Sampled-Data Control Systems},
 Springer-Verlag London Lit. 1995.

%\bibitem{C} Coron, J.M., Global asymptotic stabilization for controllable
%systems without drift, {\em Math. Control, Signals and Systems}, Vol. 5, pp.
%295-312, 1992.

\bibitem{CLA}
Colladoa, J., R. Lozanob and A. Ailon, Semi-global stabilization of
discrete-time systems with bounded inputs using a periodic
controller, {\em Systems and Control Letters}, Vol. 36, pp.
267-275, 1999.


\bibitem{CC}
Cotlar, M.  and R.Cignoli,  {\em
An Introduction to  Functional Analysis}, North Holland Publishing
Company, 1974.


\bibitem{Das} Das, S., Simultaneous  stabilization of  Two Discrete-Time
 Plants using   a 2-periodic Controller, {\it IEEE Trans. on Automatic Control,} Vol
AC-46 (2001), pp. 125-130.


\bibitem{DR} Das, S. and  P.K. Rajagopalan, Periodic Discrete-Time Systems:
Stability  Analysis and  Robust  Control  using Zero Placement, {\it IEEE Trans. on
Automatic Control,} Vol AC-37 (1992), pp. 374-378.


\bibitem{DS}
Dahleh, M.A.  and J.S. Shamma, Rejection of  persisitent  bounded disturbances:
Nonlinear  controllers, {\em System  and Control Letters }  Vol. 18 (1992)
 pp.  245-252.


\bibitem{DLMS} Desoer, C.A.. R.W. Liu, J. Murray and  R. Saeks, Feedback  System
design: the  fractional  representation  approach, {\it IEEE Trans. on Automatic
Control,} Vol AC-25 (1980), pp. 399-412.



\bibitem{FF2}
Feintuch, A. and B.A. Francis, Uniformly optimal control
of linear timevarying  systems,  {\em
System  and  Control Letters ,} Vol. 5, (1984) pp. 67-71.

\bibitem{FF}
Feintuch, A. and B.A. Francis, Uniformly optimal control
of linear feedback systems, {\em Automatica}, Vol. 21,
(1985) pp. 563-574.

\bibitem{Fr}
Francis, B.A.  A Course  in  $H_\infty$ Control  Theory, Vol. 88 in
 {\em Lecture  Notes in Control  and  Information Sciences}, Springer-Verlag, New
 York
1987.

\bibitem{FG}
Francis, B. A. and T. T. Georgiou, Stability theory
for linear time-invariant plants with periodic digital
controllers, {\em IEEE Trans. on Automatic Control,} Vol. AC-33,
(1988) pp. 820-832.


\bibitem{GE}
Godhavn, J-M.  and Olav Egeland, A Lyapunov Approach to Exponetial
Stablization of Nonholonomic Systems in Power  form, {\em IEEE Trans. on
Automatic Control,} Vol. AC-42, (1997) pp. 1028-1032.


\bibitem{GL}
Green, M. and  Limebeer, D.J.N {\em Linear Robust  Control}, Prentice  Hall, 1995.

%\bibitem{IZ}
%In, H. and C. Zhang, A multirate digital controller for model
%matching, {\em Automatica} Vol. 30, No. 6, (1994) pp. 1043-1050.

\bibitem{Ka}
Kabamba, P.T., Control of linear systems using
generalized sampled data functions, {\em IEEE Trans. on Automatic Control,}
Vol. AC-32, (1987) pp. 772-783.

\bibitem{KY}
Kabamba, P.T., and  C. Yang, Simultaneous  Controller Design  for  Linear
Time-Invariant Systems, {\em IEEE Trans. on Automatic Control,} Vol. AC-36, (1991)
pp. 106-111.


\bibitem{KN}
Kano, H. and T.Nishimura, Controllability, Stabilizability, and  matrix Riccati
equation for Periodic system, {\em IEEE Trans. on Automatic Control,} Vol. AC-30,
(1985) pp. 1129-1131.

\bibitem{Kh}
Khalil, H.  {\em Nonlinear  Systems}, Second Edition, Prentice  Hall
 1996.

\bibitem{KP}
Khargonekar, P.P., and K. Poolla, Uniformly optimal control of  linear
time-invariant plants: Nonlinear  time  varying  controllers, {\em
System  and  Control Letters ,} Vol. 6, (1986) pp. 303-308.

\bibitem{KPT}
Khargonekar, P.P., K. Poolla, and A .Tannenbaum,
Robust control of linear time-invariant plants using periodic compensation,  {\em
IEEE Trans. on Automatic Control,} Vol. AC-30, (1985) pp. 1088-1096.


\bibitem{Ko}
K\"{o}the, G.,  {\em Toplological  Vector  Spaces}, Springer  Verlag
1969, translated  from  the  German original by D.J.H. Garling.


\bibitem{Kr}
Kreyszig, E., {\em
Introductory Functional Analysis with Applications}, John Wiley \&
Sons. Inc., 1978.

\bibitem{Ku} Kucera, V., Algebraic theory of discrete control for
multivariable systems, {\em Kybernetica} Vol. 10-12, pp. 1-240, published in
installments, 1974-1976.

\bibitem{LMR}
Lee, S., S.M. Meerkov, and T. Runolfsson, (1987), Vibrational
 feedback control: zeros placement capabilities,  {\em IEEE Trans. on
Automatic Control,} Vol. AC-32, (1987) pp. 604-611.


\bibitem{LCC}
Liu, J.S., Y.S. Chou and  F.R. Chang, Decoupling  of continuous-time linear
time  invariant systems using generalized sampled-data hold functions, {\em Systems
and Control Letters}, Vol. 19, pp. 61-695, 1992.

\bibitem{PT}
Poolla, K. and T. Ting, Nonlinear time-varying controllers
for robust stabilization, {\em IEEE Trans. on Automatic
Control,} Vol. AC-32, (1987) pp. 195-200.


\bibitem{Rud}
Rudin, W.,  {\em Real and  Complex Analysis}, Third Edition, McGraw-Hill , 1986.


\bibitem{Rud2}
Rudin, W.,  {\em Principals of Mathematical Analysis}, Third Edition, McGraw-Hill ,
1976.

\bibitem{Ru}
Rugh, J.,  {\em Linear System Theory}, Second Edition, Prentice Hall, 1996.


\bibitem{SZ}
Schmid, R. and C. Zhang, Performance  Analysis  of  Periodic  control for  $l_1$ and
$l_\infty $ disturbance rejection, {\em Asian Journal of Control } Vol. 3 Number 3
 (2001)
 pp. 240-247.

\bibitem{SZ2}
Schmid, R. and C. Zhang, Performance Analysis of Periodic Control for $L_1$ and
$L_\infty$ Sampled-data  Control, {\it Proc.  IEEE Third International Conference
on  Control  Theory and Applications}, Pretoria, South Africa,  December 2001.

\bibitem{SZ3}
Schmid, R. and C. Zhang, Performance  Analysis  of  Periodic  control for  $H_2$ and
 mixed $H_2 / H_\infty $ Sampled-Data Control,   {\em The Transactions of the South
 African Institute of Electrical Engineers}, Vol. 93, No. 2, Jun. 2002, pp.73-77.

\bibitem{SZ4}
Schmid, R. and C. Zhang, Performance Analysis of Nonlinear Periodic Control for $l_p$
Disturbance Rejection,  {\it Proc.  4th  ASCC Asian Control
Conference}, Singapore, September  2002.


\bibitem{SZ5}
Schmid, R. and C. Zhang, Performance Analysis of Nonlinear Periodic Sampled-data
Controllers  for $L_p$ Disturbance Rejection,  {\it IEEE Transactions on Automatic
Control}, to appear.


\bibitem{SS}
Sezer, M.E.   and  D.Siljak, Structurally  fixed   modes {\em Systems and Control
Letters,} Vol. 1, (1981) pp. 60-64.

\bibitem{Sh}
Shamma,J.S.  Nonlinear  state  feedback  control for $l_1$ optimal  control,
{\em Systems and Control Letters,} Vol. 21, (1993) pp. 265-270.


\bibitem{SD}
Shamma, J.S. and M.A. Dahleh, Time-varying versus time-invariant
compensation for rejection of persistent bounded disturbances
and robust stabilization, {\em IEEE Trans. on Automatic
Control,} Vol. AC-36, (1991) pp. 838-847.

\bibitem{SL}
Shujaee, K and B. Lehman, Vibrational  Feedback  control of  Time  delay  systems,
{\em IEEE Trans. on Automatic Control,} Vol. AC-42, (1997) pp. 1529-1545.


\bibitem{Si}
Simmons. G.F.,  {\em Introduction  to Toplogy and  Modern Analysis},  McGraw-Hill
1963.

\bibitem{St}
Stoorvogel, A.A.,  Nonlinear $L_1$ optimal  controllers  for Linear Systems,
{\em IEEE Trans. on Automatic Control,} Vol. AC-40, (1995) pp. 694-696.

\bibitem{St2}
Stoorvogel, A.A., The  Robust $H_2$ Control Problem: A Worst-Case Design,
{\em IEEE Trans. on Automatic Control,} Vol. AC-38, (1993) pp. 1358-1370.

\bibitem{TZZ}
Tarn, T.J., J.R. Zavgren  and X. Zeng, Stabilization of Infinite-dimensional Systems
with Periodic Feedback  Gains and  Sampled Output, {\em Automatica}, Vol. 24, pp.
95-99, 1988.


\bibitem{TTT}
Trave, L., A.M. Tarras and  A. Titli,  An Application of  Vibrational  Control to
Cancel  Unstable  Decentralized  Fixed Modes, {\em IEEE Trans. on Automatic Control,}
Vol. AC-30, (1985) pp. 283-286.


\bibitem{V}
Vidyasagar, M.,  {\em Nonlinear Systems Analysis},  Prentice
Hall, 1978.


\bibitem{Wei}
Wei, K., The  solution of  a  treanscendental problem and its  application  in
simultaneous stabilization problems,  {\em IEEE Transactions on Automatic Control},
Vol. 37, pp. 1305-1315, 1992.


\bibitem{W}
Willems, J., Time-varying  Feedback  for the  Stablization  of Fixed Modes in
Decentralized Control  systems, {\em Automatica}, Vol. 25, pp. 125-131, 1989.


\bibitem{YW93}
Yen, N.Z. and Y.C. Wu, Optimal periodic control implemented as a
generalized sampled-data hold output feedback control,  {\em IEEE
Transactions on Automatic Control}, Vol. 38, pp. 1560-1563, 1993.


\bibitem{YJB} Youla, D.C., H.A. Jabr, and J.J. Bongiorno Jr., Modern
Wiener-Hopf design of optimal controllers: Part II, {\em IEEE Trans. on Automatic
Control,} Vol. AC-21, pp. 319-338, 1976.



\bibitem{Za} Zames, G., Feedback  and  optimal sensitivity: Model reference
transformations, multiplicative  seminorms and  approximate  inverses, {\em IEEE
Trans. on Automatic Control,} Vol. AC-26, pp. 301-320, 1981.


%\bibitem{Zh}
%Zhang, C., A dual rate compensator for system loop
%zero assignment,
%{\em Systems and Control Letters,} Vol. 19, (1992) pp. 225-232.

%\bibitem{ZB}
%Zhang, C., and V. Blondel, Simultaneous stabilization using an LTI
%compensator and a sampler and hold, Int. J. Control,  Vol. 57, No. 2,
%(1993) pp. 293 - 308.


\bibitem{ZZ}
Zhang, C., and J. Zhang, Performance Analysis of Periodically Time-Varying
Controllers for Sampled Data Control,
{\em IEEE transactions on  Automatic Control } Vol. 44, no.8,  (1999)
pp 1607-1611.

\bibitem{ZZ2}
Zhang, C., and J. Zhang, $H_2$ performance of continuous time periodically  time
varying controllers, {\it Systems and Control Letters,} Vol. 32, (1997) pp. 209-221.

\bibitem{ZZS}
Zhang, C., J. Zhang, and  R. Schmid,  On $l_p$ disturbance rejection using
periodic feedback  control, {\em System  and Control Letters } Vol. 38 (1999)
227-234.

\bibitem{ZZF}
Zhang, C., J. Zhang, and K. Furuta, Analysis of $H_2$ and
$H_\infty$ performance of discrete periodically time varying controllers,
{\em Automatica}, Vol. 33, pp. 619-634, 1997.

\end{thebibliography}

